### 2019-01-04 papers/journal/experiments.tex
minor edit

The minimal connectivity results for each variation of the existential condition is presented in table~\ref{tab:smt-grph}.
%
No matter what the rules of molecular
interactions and regulation, steady state requires the graph structure to be at least strongly connected, and therefore 2-connected.
%
Beyond this, we find that 3-connectedness is existential condition for the Boolean regulation model on vesicles, while 4-connectedness is necessary and sufficient for the more constrained SNARE-SNARE inhibition on vesicles and Boolean regulation on compartments.
%
For more constrained regulation models
(including the case where SNAREs are always active) we did not find any possible graphs
representing steady state vesicle transport networks. 
%
This strongly suggests (but does not
prove, since we only checked graphs of finite size) that no such graphs exist.
%We have found no graphs for Variants A where no regulation is enforced on the activity of the molecules both on the edges and nodes.
%%
%Two other cases Variant B, Variant E also results in the no graph satisfying the constraints.
%%  
%2-connectedness is the existential condition for Variants D where activity of the molecule is dependent on the presence of the other molecules. 
%%
%Variants C has 3-connectedness as

>>>>

The minimal connectivity results for each variation of the existential condition is presented in table~\ref{tab:smt-grph}.
%
%No matter what the rules of molecular interactions and regulation, steady state requires the graph structure to be at least strongly connected, and therefore 2-connected.
The steady-state constraint requires that structure of the graph is at least 2-connected. 
%
We found that 3-connectedness is the existential condition for the Boolean regulation model on vesicles, while 4-connectedness is the existential condition for the more constrained SNARE-SNARE inhibition on vesicles and Boolean regulation on compartments.
%Beyond this, we find that 3-connectedness is existential condition for the Boolean regulation model on vesicles, while 4-connectedness is existential condition for the more constrained SNARE-SNARE inhibition on vesicles and Boolean regulation on compartments.
%
For more constrained regulation models
(including the case where SNAREs are always active) we did not find any possible graphs
representing steady state vesicle transport networks. 
%
This strongly suggests (but does not
prove, since we only checked graphs of finite size) that no such graphs exist.
%We have found no graphs for Variants A where no regulation is enforced on the activity of the molecules both on the edges and nodes.
%%
%Two other cases Variant B, Variant E also results in the no graph satisfying the constraints.
%%  
%2-connectedness is the existential condition for Variants D where activity of the molecule is dependent on the presence of the other molecules. 
%%
%Variants C has 3-connectedness as
